Defining Greatness

### 2024-11-30 paper/paper.qmd
minor change to paper
some more edits to paper

---
title: "Defining Greatness"
subtitle: "A Comparative Analysis of Tom Brady and Patrick Mahomes"
author: 
  - Alexander Guarasci
thanks: "Code and data are available at: https://github.com/AlexanderG123/nfl"
date: today
date-format: long
abstract: "This paper compares NFL quarterbacks Tom Brady and Patrick Mahomes, focusing on their statistical performances. Analyzing their respective career data, this paper uses predictive modelling to forecast Patrick Mahomes future. It finds that while both have impressive career statistics, ultimately, playoff victories, particularly Super Bowl wins, serve as a more definitive measure of greatness. By examining these players, the paper highlights how the NFL’s dynamic context impacts player evaluation and legacy assessment."
format: 
  pdf: 
    fig-pos: "H"
number-sections: false
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

To answer this question, this analysis draws on statistical data, examining past performance, and broader career trajectories. It evaluates what each quarterback has achieved to date and aims to project Patrick Mahomes future.

The findings reveal that Brady’s legacy is unparalleled in its longevity and sheer accomplishment, while Mahomes’ career trajectory suggests he does have the potential to surpass Brady, it is highly unlikely that he does from a statistical standpoint. These insights are significant not only for appreciating their contributions to football but also for understanding the broader implications of what society values in its icons.

The paper is structured as follows: the first section provides an explanation of the data used in this paper, what it shows and where it comes from. The second section discusses the model used to predict the future of Patrick Mahomes career. The third section shows the results of the model. The final section discusses the implication of the model as well as provides more insight into the two players legacies.

@@

The data used in this analysis originates from nflverse [@citenflverse], a comprehensive collection of packages tailored for National Football League (NFL) data. These packages aggregate statistics, player information, and game results spanning several decades. For this paper, the focus was narrowed to quarterback (QB) performance data, specifically for Tom Brady and Patrick Mahomes.

@@

Despite Mahomes’ impressive projected stats, Brady’s career longevity and overall impact on the game have allowed him to achieve these remarkable milestones. Mahomes will need to maintain his performance over a long period to catch up to Brady’s cumulative totals. Brady’s consistency and durability throughout his career, as seen in his passing and rushing stats, have firmly established him as one of the greatest quarterbacks in NFL history. Mahomes, on the other hand, shows great potential and is already a future first balot Hall of Famer, but he has yet to match Brady’s career volume.

>>>>

---
title: "Defining Greatness"
subtitle: "A Comparative Analysis of Tom Brady and Patrick Mahomes"
author: 
  - Alexander Guarasci
thanks: "Code and data are available at: https://github.com/AlexanderG123/nfl"
date: today
date-format: long
abstract: "This paper compares National Football League (NFL) quarterbacks Tom Brady and Patrick Mahomes, focusing on their statistical performances. Analyzing their respective career data, this paper uses predictive modelling to forecast Patrick Mahomes’ future. It finds that while both have impressive career statistics, ultimately, playoff victories, particularly Super Bowl wins, serve as a more definitive measure of greatness. By examining the performance of these players, the paper highlights how the NFL’s dynamic context impacts player evaluation and legacy assessment."
format: 
  pdf: 
    fig-pos: "H"
number-sections: false
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

To answer this question, this analysis draws on statistical data, examining past performance, and broader career trajectories. It evaluates what each quarterback has achieved to date and aims to project Patrick Mahomes’ future.

The findings reveal that Brady’s legacy is unparalleled in its longevity and sheer accomplishment. While Mahomes’ career trajectory suggests he does have the potential to surpass Brady, it is highly unlikely that he does from a statistical standpoint. These insights are significant not only for appreciating their contributions to football but also for understanding the broader implications of what society values in its icons.

The paper is structured as follows: the first section provides an explanation of the data used in this paper, what it shows and where it comes from. The second section discusses the model used to predict the future of Patrick Mahomes’ career. The third section shows the results of the model. The final section discusses the implication of the model as well as provides more insight into the two players’ legacies.

@@

The data used in this analysis originates from nflverse [@citenflverse], a comprehensive collection of packages tailored for NFL data. These packages aggregate statistics, player information and game results spanning several decades. For this paper, the focus was narrowed to quarterback (QB) performance data, specifically for Tom Brady and Patrick Mahomes.

@@

Despite Mahomes’ impressive projected stats, Brady’s career longevity and overall impact on the game have allowed him to achieve these remarkable milestones. Mahomes will need to maintain his performance over a long period to catch up to Brady’s cumulative totals. Brady’s consistency and durability throughout his career, as seen in his passing and rushing stats, have firmly established him as one of the greatest quarterbacks in NFL history. Mahomes, on the other hand, shows great potential and is already a future first ballot Hall of Famer, but he has yet to match Brady’s career volume.
